Joint Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-02-21 src/tex/ms.tex
[showyourwork] overleaf sync

 \begin{figure}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping quadratic patches of size $8\times8$~pixels on top of an example image of the size $128 \times 68$~pixels. The overlap size was chosen to be $2$ pixels, which results in 50 patches in total. The patches are shown translucent, such that the horizontal and vertical \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners. The bottom row shows the red example patch $\mathbf{x}_n$ on the left. The three other patches show the quantity $\Sigma_{k} \mathbf{x}_n$, which is the result of the patch represented in the Eigenbasis of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$. This example uses the GMM learned from the JWST Cas A image.
            }
            \label{fig:patches}
            \script{patches.py}
        \end{centering}
    \end{figure}

>>>>

 \begin{figure}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/patches.pdf}
            \caption{
                Grid of overlapping quadratic patches of size $8\times8$~pixels on top of an example image of the size $128 \times 68$~pixels. The overlap size was chosen to be $2$ pixels, which results in 50 patches in total. The patches are shown translucent, such that the horizontal and vertical \enquote{stripes} result from two neighboring overlapping patches, while the small, even lighter squares result from four patches overlapping at the their corners. The bottom row shows the red example patch $\mathbf{x}_n$ on the left. The three other patches show the example patch represented by a linear combination of the six largest Eigenvectors of the covariance matrices of the 3 most likely GMM components $k = 105, 77, 17$. This example uses the GMM learned from the JWST Cas A image.
            }
            \label{fig:patches}
            \script{patches.py}
        \end{centering}
    \end{figure}
